---
title: "ASSIGNMENT-4"
author: "vivek rao kathheragandla"
date: "2024-03-12"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library("tidyverse")
library("ISLR")
library("factoextra")
library("flexclust")
library("ggplot2")
library("dplyr")
library("caret")
```

#applying the knit functions
```{r}
data_pharma <- read.csv("C:\\Users\\KATHHERAGANDLA VIVEK\\OneDrive\\Documents\\FML\\Assignment_4\\Pharmaceuticals (1).csv") 
head(data_pharma)
summary(data_pharma)
```
***
##QUESTION-A - Use only the numerical variables (1 to 9) to cluster the 21 firms. Justify the 
various choices made in conducting the cluster analysis, such as weights for different variables, the specific clustering algorithm(s) used, the number of clusters formed, and so on.
```{r}
#Performing z-score scaling for the pahrmaceuticals dataframe 
Scaling_pharma_data <- scale(data_pharma[,3:11])
summary(Scaling_pharma_data)
```
```{r}
#Performing range scaling for the the dataframe 
range_pharma <- scale(data_pharma[,3:11])
#summarizing the scaled data frame
summary(range_pharma)
```

```{r}
#applying K-means clustering for the scaled data
kmeans_1 <- kmeans(Scaling_pharma_data, centers = 5, nstart = 25)
#visualizing the clusters on agraph
fviz_cluster(kmeans_1, data = Scaling_pharma_data)

```
```{r}
#Assuming kmeans_1 contains the results of your k-means clustering
print(kmeans_1)
```
##OVERVIEW of the K-means Clustering:-
##The summary function performed on the k-means data gives the infromation on 9 variables for the 21 pharmaceutical companies. There are a total of 5 clusters with 5 centeroid points and the sizes of the clusters are (2, 3, 4, 4, 8).

***
##QUESTION-B - Interpret the clusters with respect to the numerical variables used in forming the clusters.

```{r}
#plotting the number of clusters vs the total value
fviz_nbclust(Scaling_pharma_data, kmeans, method = "wss")
```
** Here in this plot we can clearly see that the graph is not forming an elbow shape and it is getting flattened slightly at k=4 and k=6
```{r}
#figuring ou the number of optimal clusters by plotting the number of clusters
#against average silhoutte width
fviz_nbclust(Scaling_pharma_data, kmeans, method = "silhouette")
```

##By judging from the silhoutte graph we easily conclude that 5 clusters is the best and optimal solution for this k-means clustering.

***

##QUESTION-C - Is there a pattern in the clusters with respect to the numerical variables (10 
to 12)? (those not used in forming the clusters)
```{r}
#Calculating the mean value from the actual data that is plotted in the clusters
#perfroming the aggregate function for the pharma data
aggregate(data_pharma[3:11], by=list(cluster=kmeans_1$cluster), mean)

```
```{r}
#perfroming the merging of the data frames using cbind
temp_data <- cbind(data_pharma, cluster = kmeans_1$cluster)
tibble(temp_data)
```

```{r}
#Summarizing the detailed beakdown by cluster
by(temp_data, factor(temp_data$cluster), summary)
```
```{r}
#median calculation 
recommend_table <- table(temp_data$cluster, temp_data$Median_Recommendation)
names(dimnames(recommend_table)) <- c("Cluster", "Recommendation")
recommend_table <- addmargins(recommend_table)
recommend_table
```

##One strong buy, seven moderate buys, nine holds, and four moderate sells make the total number of 21 recommendations. All four recommendations, including the opposite advice on buys and sells, are mixed together in Cluster 5. Only mod purchase and hold information can be found in Clusters 1, 2, and 3.Both a moderate buy and moderate sell recommendation are present for Cluster 4.
```{r}
#Location of firm headquarter's breakdown of clusters based on the merged data
location_data <- table(temp_data$cluster, temp_data$Location)
names(dimnames(location_data)) <- c("Cluster", "Location")
location_data <- addmargins(location_data)
location_data
```
##There are 21 firms in all, with 13 in the US, 3 in the UK, and 1 each in Canada, France,Germany,Ireland, and Switzerland. US, UK, and Switzerland are all featured in Cluster 5. Germany and the US are in Cluster 2. US and Canada are in Cluster 1. 
US and Britain are in Cluster 3.The US, France, and Ireland make up Cluster 4.
```{r}

#summarizing the stock exchange values for each cluster
#creating a data frame for the merged data and initializing the exchange table
exchange_table <- table(temp_data$cluster, temp_data$Exchange)
names(dimnames(exchange_table)) <- c("Cluster", "Exchange")
exchange_table <- addmargins(exchange_table)
exchange_table
```
##There are 21 companies overall, divided into 1 Amex, 1 Nasdaq, and 19 NYSE. Cluster 5 just has the NYSE. All three are in Cluster 2. clusters 1,3,4 all contains only NYSE.

***

##QUESTION-D - Provide an appropriate name for each cluster using any or all of the 
variables in the dataset.

ANSWER :- 
Cluster 1: - The cluster 3 can be named as “Small_Net_Profit_Margin-High PE 
ratio”. All are NAM companies.

Cluster 2: The cluster number 2 can be named “Low_Market_Cap & Less_ROA” - Hold or Buy 
exchanges.

Cluster 3: The cluster 4 can be named “High Market Cap - more RoE - more RoA- High Asset 
Turnover- more NetProfitMargin” - All are the Hold or Buy US companies that are part of 
NYSE.

Cluster 4: The cluster 4 can be named as “least PE ratio & low RoE & Minimum Asset 
Turnover- High revenue growth - mixed recommendation. All are US or European 
companies that belongs to NYSE.

Cluster 5: The cluster number 5 can be named as “Least_Revenue_growth”. It mostly 
comprised of US companies and all are NYSE.

##Also Trying or Exploring the other algorithms whether they can perform better 
clustering or not? 
```{r}
#Assuming range_pharma is your pharmaceutical dataset
#Visualize the number of clusters using the silhouette method with k-means
fviz_nbclust(range_pharma, FUN = kmeans, method = "silhouette")
```

```{r}
#Assuming range_pharma_data is your pharmaceutical dataset
#Visualize the number of clusters using the within-cluster sum of squares method with k-means
fviz_nbclust(range_pharma, kmeans, method = "wss")
```

PLOTTING THE KMEANS AND THE CLUSTERS

```{r}
# Perform kernel k-means clustering
kmeans_2 = kcca(Scaling_pharma_data, k=5, kccaFamily("kmeans"))
kmeans_2
```

```{r}
# Extract cluster assignments from the kernel k-means clustering object
clusters(kmeans_2)
```

```{r}
#Applying the predict() function
clusters_index <- predict(kmeans_2)
image(kmeans_2)
points(Scaling_pharma_data, col=clusters_index, pch=19, cex=1.0)
```

##Instead of utilising the kmeans function from base R, we perform a kmeans cluster on k = 5 here utilising the kcca method. In comparison to the base R method, the clustering has the same size but a distinct assignment between the points. The clustering graph shows that there is more ambiguity in the grouping than we would want, especially between groups 1, 2, and 3.

PLOTTING THE KMEDIANS AND THE CLUSTERS.
```{r}
# Perform kernel k-means clustering with k-medians algorithm
kmeans_2 = kcca(Scaling_pharma_data, k=5, kccaFamily("kmedians"))
kmeans_2
```

```{r}
# Extract cluster assignments from the kernel k-means clustering object
clusters(kmeans_2)
```

```{r}
# Predict cluster assignments for each data point
clusters_index <- predict(kmeans_2)
# Plot the image representation of the clustering
image(kmeans_2)
# Add points to the plot with cluster assignments
points(Scaling_pharma_data, col=clusters_index, pch=19, cex=1.0)
```

##The five clusters have sizes of 4, 5, 3, 3, and 6 if we convert the KCC to Kmeans. However, the clustering is less noticeable. Although we are looking into the additional data to see if there are any better methods or resources we can employ to improve the visual cluster, it's not obvious if a better cluster is truly possible.